Parameter-less Population Pyramid

### 2014-01-28 Parameterless Population Pyramid/main.tex
Word tweaks in abstract.

\maketitle
\begin{abstract}
%Maximum 200 Words
  Real world applications of evolutionary techniques are often
  hindered by the need to determine problem specific parameter
  settings.  While some previous methods have reduced or removed the
  need for parameter tuning, many do so by trading efficiency for
  general applicability.  The Parameter-less Population Pyramid (P3)
  is an evolutionary technique that both requires \textbf{no parameters}
  and is broadly effective. P3 strikes a balance between
  continuous integration of diversity with exploitative elitist
  operators, allowing it to solve easy problems quickly and hard
  problems eventually.  When compared with three optimally tuned,
  state of the art optimization techniques, P3 always finds the
  optimum at least a constant factor \emph{\textbf{faster}} across
  four benchmarks (Deceptive Trap, Deceptive Step Trap,
  HIFF, Rastrigin).  More importantly, on three
  randomized benchmarks (NK Landscapes, Ising Spin Glasses, MAX-SAT),
  P3 has a lower order of computational complexity as measured by
  evaluations.
  We also provide outlines for expected runtime analysis of P3,
  setting the stage for future theory based conclusions.
  Based on over 1 trillion evaluations, our results
  suggest P3 has wide applicability to a broad class of
  problems.
\end{abstract}

>>>>

\maketitle
\begin{abstract}
%Maximum 200 Words
  Real world applications of evolutionary techniques are often
  hindered by the need to determine problem specific parameter
  settings.  While some previous methods have reduced or removed the
  need for parameter tuning, many do so by trading efficiency for
  general applicability.  The Parameter-less Population Pyramid (P3)
  is an evolutionary technique that requires \textbf{no parameters}
  and is still broadly effective. P3 strikes a balance between
  continuous integration of diversity and exploitative elitist
  operators, allowing it to solve easy problems quickly and hard
  problems eventually.  When compared with three optimally tuned,
  state of the art optimization techniques, P3 always finds the
  optimum at least a constant factor \emph{\textbf{faster}} across
  four benchmarks (Deceptive Trap, Deceptive Step Trap,
  HIFF, Rastrigin).  More importantly, on three
  randomized benchmarks (NK Landscapes, Ising Spin Glasses, MAX-SAT),
  P3 has a lower order of computational complexity as measured by
  evaluations.
  We also provide outlines for expected runtime analysis of P3,
  setting the stage for future theory based conclusions.
  Based on over 1 trillion evaluations, our results
  suggest P3 has wide applicability to a broad class of
  problems.
\end{abstract}
